Bird beak's elaboration and exploration

### 2022-10-17 Analysis/11-variance_partitioning.Rmd
Update 11-variance_partitioning.Rmd

@@

@@

@@

Here the model is highly dimensional and the terms sample sizes vary by two orders of magnitude.

This script is a working script to run the chains on the SHARC Sheffield cluster.

```{r load_packages, eval = TRUE, message = FALSE}
set.seed(42)
## Loading beer
library(mcmcmcglmmm)
library(MCMCglmm)
library(dispRity)

## Loading the parametrisation data
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order.rda")

## Select the data
shapespace <- shapespace_allbirds_lvl_superorder_order[[1]]$space
selected_dim <- shapespace_allbirds_lvl_superorder_order[[1]]$dimensions
consensus_tree <- shapespace_allbirds_lvl_superorder_order[[1]]$consensus_tree
trees_list <- shapespace_allbirds_lvl_superorder_order[[1]]$trees_list
```

# All birds shapespace analyses

## Mini-chains parametrization

Making a 2D model with just the super order random terms

```{r, parametrise_the_model, eval = FALSE}
## Set up the parametrising chains models
param_MCMCglmm <- make.mini.chains(data         = shapespace,
                                   dimensions   = selected_dim,
                                   tree         = consensus_tree,
                                   trait.family = "gaussian",
                                   randoms      = c("global", "level1", "level2"),
                                   residuals    = "global",
                                   priors       = 0.02,
                                   verbose      = TRUE,
                                   parameters   = list(
                                       nitt   = 20000,
                                       thin   = 500,
                                       burnin = 0))
save(param_MCMCglmm, file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_2D_9levels_20k.rda")
```

## Running the parametrisation chains (for the small model)

```{r}
library(mcmcmcglmmm)
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_2D_9levels_20k.rda")
## Running the three MCMCglmm models
start <- Sys.time()
params_shapespace_2D_9levels_20k <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(params_shapespace_2D_9levels_20k, file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_2D_9levels_20k_chain1.rda")
end <- Sys.time()
end - start
```

```{r}
library(mcmcmcglmmm)
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_2D_9levels_20k.rda")
## Running the three MCMCglmm models
start <- Sys.time()
params_shapespace_2D_9levels_20k <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(params_shapespace_2D_9levels_20k, file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_2D_9levels_20k_chain2.rda")
end <- Sys.time()
end - start
```

```{r}
library(mcmcmcglmmm)
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_2D_9levels_20k.rda")
## Running the three MCMCglmm models
start <- Sys.time()
params_shapespace_2D_9levels_20k <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(params_shapespace_2D_9levels_20k, file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_2D_9levels_20k_chain3.rda")
end <- Sys.time()
end - start
```

## (for the big model)

```{r}
library(mcmcmcglmmm)
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_8D_32levels_20k.rda")
## Running the three MCMCglmm models
start <- Sys.time()
params_shapespace_8D_32levels_20k <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(params_shapespace_8D_32levels_20k, file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_8D_32levels_20k_chain1.rda")
end <- Sys.time()
end - start
```

```{r}
library(mcmcmcglmmm)
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_8D_32levels_20k.rda")
## Running the three MCMCglmm models
start <- Sys.time()
params_shapespace_8D_32levels_20k <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(params_shapespace_8D_32levels_20k, file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_8D_32levels_20k_chain2.rda")
end <- Sys.time()
end - start
```

```{r}
library(mcmcmcglmmm)
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_8D_32levels_20k.rda")
## Running the three MCMCglmm models
start <- Sys.time()
params_shapespace_8D_32levels_20k <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(params_shapespace_8D_32levels_20k, file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_8D_32levels_20k_chain3.rda")
end <- Sys.time()
end - start
```

From these three chains, we first extracted the three burnin periods (defined as the generation when the chain reaches the median likelihood value times 1.25).
We then extracted the posterior estimates of the R-Structure, G-Structure and fixed effects (mean and covariance) (ignoring the runs from the previously estimated burnin periods) to serve as our priors for our mini-chains. 
For those values, we took the highest burnin as the overall burnin and the median of the three posteriors as the overall priors.

```{r, get_model_parameters, eval = FALSE}
## Load the computed models
param_chains <- list()
for(i in 1:3) {
    load(paste0("../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_2D_9levels_20k_chain", i, ".rda"))
    param_chains[[i]] <- params_shapespace_2D_9levels_20k[[1]]
}
## Extract the parameters from the parameter chains
est_params <- extract.parameters(param_chains)
```

### Running the mini-chains

```{r, set_the_mini_chains, eval = FALSE}
## The thinning parameter
thin <- 200
## The number of samples per chains
samples <- 10

## Set up the mini-chains models
shapespace_allbirds_lvl_superorder_order_2D <- make.mini.chains(
                                data         = shapespace,
                                dimensions   = 1:2,
                                tree         = trees_list[sample(1:1000, 1000)],
                                trait.family = "gaussian",
                                randoms      = c("global", "level1"),
                                residuals    = "global",
                                priors       = est_params$priors,
                                verbose      = TRUE,
                                parameters   = list(
                                    nitt   = est_params$burnin + thin * samples,
                                    thin   = thin,
                                    burnin = est_params$burnin))
## Save the mini.chains
save(shapespace_allbirds_lvl_superorder_order_2D, file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/shapespace_allbirds_lvl_superorder_order_2D.mini.chains")
```

The chains are then run on the cluster
TODO: details

```{r}
library(mcmcmcglmmm)
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/shapespace_allbirds_lvl_superorder_order_2D.mini.chains")
## Running the three MCMCglmm models
start <- Sys.time()
shapespace_allbirds_lvl_superorder_order_2D <- run.mini.chains(shapespace_allbirds_lvl_superorder_order_2D, replicates = 20)
save(shapespace_allbirds_lvl_superorder_order_2D, file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_2D_9levels_20k_chain1_20.rda")
end <- Sys.time()
end - start
```

### Combining the model data

```{r, eval = FALSE}
## Set up the variables
models_path <- "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/cluster/"
## Getting all the model files
model_files <- list.files(models_path, pattern = ".rda")

## Check if the model exists already
if(!("shapespace_allbirds_lvl_superorder_order.MCMCglmm" %in% list.files("../Data/Processed/"))) {
    ## Preparing the model files
    model_list <- list()
    class(model_list) <- c("beer", "mini.chains")
    ## Get the first model
    load(paste0(models_path, model_files[1], collapse = "/"))
    ## Move it to the storage
    system(paste("mv", paste0(models_path, model_files[1]), paste0(models_path, "done/")))
    print(model_files[1])
    ## Clean the bits that are not going to be used (but are huge)
    model[[1]][c("error.term", "family", "y.additional", "ginverse", "ZR")] <- NULL
    ## Update the model list
    model_list[[length(model_list)+1]] <- model[[1]]
    model <- NULL
    model_files <- model_files[-1]
} else {
    ## Updating the model
    load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order.MCMCglmm")
    model_list <- shapespace_allbirds_lvl_superorder_order
}

## Get the subsequent models and merge them as we go
while(length(model_files) != 0) {
    load(paste0(models_path, model_files[1], collapse = "/"))
    ## Move it to storage
    system(paste("mv", paste0(models_path, model_files[1]), paste0(models_path, "done/")))
    print(model_files[1])
    ## Clean the bits that are not going to be used (but are huge)
    model[[1]][c("error.term", "family", "y.additional", "ginverse", "ZR")] <- NULL
    ## Update the model list
    model_list[[length(model_list)+1]] <- model[[1]]
    ## Merge the models (overwrite the model list)
    model_list <- list(combine.mini.chains(model_list))
    ## DEBUG
    print("model list size:")
    print(format(object.size(model_list), units = "MB"))
    model <- NULL
    model_files <- model_files[-1]
}

## Combining the model files
shapespace_allbirds_lvl_superorder_order <- model_list

## Saving the results
save(shapespace_allbirds_lvl_superorder_order, file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order.MCMCglmm")

```

# Analysing the variance per terms

```{r}
## Get the variance for each level
variance_per_clades <- MCMCglmm.variance(shapespace_allbirds_lvl_superorder_order, scale = TRUE)
## Rename the columns
colnames(variance_per_clades) <- c(levels(shapespace$level1)[-1], levels(shapespace$level2)[-1], "phylogeny", "residuals")
reorder_clades <- c(9:35,1:8, 36, 37)
# ## Pull by term
# variance_per_levels<- cbind("orders" = apply(variance_per_clades[, 9:35], 1, sum),
#                             "super-orders" = apply(variance_per_clades[, 1:8], 1, sum),
#                             "phylogeny" = variance_per_clades[, 36],
#                             "residuals" = variance_per_clades[, 37])
# variance_per_terms <- cbind("clades" = apply(variance_per_clades[, 1:35], 1, sum),
#                             "phylogeny" = variance_per_clades[, 36],
#                             "residuals" = variance_per_clades[, 37])
# ## Plot the results
# pdf(file = "../Manuscript/Figures/variance_per_levels_whole_tree.pdf", height = 8, width = 14)
# par(mar = c(5,8,2,2), mfrow = c(1, 3))
# # boxplot(variance_per_terms, horizontal = TRUE, las = 1, main = "Scaled variance by terms", xlab = "Scaled variance\n(sum of each VCV variance part (diagonal))")
# # boxplot(variance_per_levels, horizontal = TRUE, las = 1, main = "Scaled variance by levels", xlab = "Scaled variance\n(sum of each VCV variance part (diagonal))")
# boxplot(variance_per_clades[,reorder_clades], horizontal = TRUE, las = 1, main = "Scaled variance by clades", xlab = "Scaled variance\n(sum of each VCV variance part (diagonal))")
# boxplot(log(variance_per_clades[,reorder_clades])/log(sample_sizes), horizontal = TRUE, las = 1, main = "Scaled variance by clades (removing sample size effect)", xlab = "Scaled variance\n(sum of each VCV variance part (diagonal))")
# boxplot(log(variance_per_clades[,reorder_clades])/log(observed_variance)[names(variances)], horizontal = TRUE, las = 1, main = "Scaled variance by clades (removing variance effect)", xlab = "Scaled variance\n(sum of each VCV variance part (diagonal))")
# dev.off()

# ## Getting the variances per clades
# variances <- apply(variance_per_clades[,reorder_clades], 2, mean)

# ## Getting the sample sizes per clades (the one for the residuals is the whole tree size)
# sample_sizes <- c("residuals" = size.subsets(order_shapespace)[28],
#                   size.subsets(superorder_shapespace),
#                   size.subsets(order_shapespace))[names(variances)]

# ## Measuring the variance for each clade and for the residuals
# ## the obs variance of the residuals is just the variance in the whole dataset (phylogeny)
# observed_variance <- c("residuals" = unlist(get.disparity(dispRity(order_shapespace, metric = sd)))[28], 
#                        unlist(get.disparity(dispRity(superorder_shapespace, metric = sd))),
#                        unlist(get.disparity(dispRity(order_shapespace, metric = sd)))[-28])^2

# plot(log(variances)/log(sample_sizes), log(sample_sizes), xlab = "log variance / log n", ylab = "log n")

```

## Standard error per terms

```{r}

## Get the number of observations per groups
variance_per_clades <- MCMCglmm.variance(shapespace_allbirds_lvl_superorder_order, scale = FALSE)
colnames(variance_per_clades) <- c(levels(shapespace$level1)[-1], levels(shapespace$level2)[-1], "phylogeny", "residuals")

## Converting into standard errors
get.se <- function(var, n) {
    sqrt(var[[1]])/sqrt(n)
}
## Get the se per group
se_per_clades <- mapply(get.se, apply(variance_per_clades, 2, list), as.list(c(size.subsets(superorder_shapespace)[-9], size.subsets(order_shapespace), "residuals" = 8748)))
## Scale that
se_per_clades <- se_per_clades/rowSums(se_per_clades)
## Get the other levels
se_per_levels<- cbind("orders" = apply(se_per_clades[, 9:35], 1, sum),
                      "super-orders" = apply(se_per_clades[, 1:8], 1, sum),
                      "phylogeny" = se_per_clades[, 36],
                      "residuals" = se_per_clades[, 37])
se_per_terms <- cbind("clades" = apply(se_per_clades[, 1:35], 1, sum),
                      "phylogeny" = se_per_clades[, 36],
                      "residuals" = se_per_clades[, 37])

## Plot the results
pdf(file = "../Manuscript/Figures/se_per_levels_whole_tree.pdf", height = 8, width = 14)
par(mar = c(5,8,2,2), mfrow = c(1, 3))
boxplot(se_per_terms, horizontal = TRUE, las = 1, main = "Scaled standard error by terms", xlab = "Scaled se ")
boxplot(se_per_levels, horizontal = TRUE, las = 1, main = "Scaled standard error by levels", xlab = "Scaled se")
boxplot(se_per_clades[,reorder_clades], horizontal = TRUE, las = 1, main = "Scaled standard error by clades", xlab = "Scaled variance")
dev.off()
```

>>>>

Here I'm just doing a one dimensional model of a one dimensional trait (BM) and two clades (`"s"` and `"t"`).

```{r, echo = FALSE}
## Setting the data
set.seed(0)
data_1 <- drop.fossil.dads(dads(stop.rule = list(max.living = 20), traits = make.traits()))
data_2 <- drop.fossil.dads(dads(stop.rule = list(max.living = 20), traits = make.traits()))

## Renaming the tips and data in data_2
rownames(data_2$data)[match(data_2$tree$tip.label, rownames(data_2$data))] <- gsub("t", "s", data_2$tree$tip.label)
data_2$tree$tip.label <- gsub("t", "s", data_2$tree$tip.label)
data_1$tree$node.label <- data_2$tree$node.label <- NULL

## Combine the trees
ultrametric_tree <- chronos(multi2di(bind.tree(data_1$tree, data_2$tree)))
class(ultrametric_tree) <- "phylo"
tree <- slide.nodes(ultrametric_tree, node = 42, slide = 0.2)

## Combine the data
data <- c(data_1$data[match(data_1$tree$tip.label, rownames(data_1$data)), ], data_2$data[match(data_2$tree$tip.label, rownames(data_2$data)), ])
data <- as.data.frame(matrix(data, ncol = 1, dimnames = list(c(names(data)), c("variable"))))
data <- cbind(data, "var2" = rnorm(40), "clade" = as.factor(c(rep("t", 20), rep("s", 20))), "animal" = rownames(data))
```

We will now run it as the following model:

```
data ~ residuals + random.phylo + random.clade_s + random.clade_t
```

```{r, echo = FALSE, message = FALSE}
## Setting up the model
first_model <- make.mini.chains(data, dimensions = c(1:2), tree = tree, trait.family = "gaussian", residuals = "global", randoms = c("global", "clade"), verbose = TRUE, parameters =  list(nitt = 20000))

## running the first model
first_model_run <- run.mini.chains(first_model, replicates = 1)[[1]]
```

And this is what it looks like graphically

```{r, echo = FALSE}
## Model object
first_model_results <- MCMCglmm.subsets(
      data          = data,
      posteriors    = first_model_run,
      group         = MCMCglmm.levels(first_model_run)[c(1:3)],
      rename.groups = c("clade_s", "clade_t", "phylogeny"))

## Set the clade colours
clade_cols <- c("clade_s" = "blue", "clade_t" = "orange", "phylogeny" = "grey")

## Plotting the model
covar.plot(first_model_results, col = clade_cols, ellipses = mean, legend = TRUE)
```
We can then extract the variance of the model:

```{r, echo = FALSE}
#@ name plot.decompose.var
#@ description plotting the variance of a model in different ways
#@ param data a dispRity object
#@ param posteriors a MCMCglmm object
#@ param group.cols the colours for each term
#@ param obs.col the colour for the observed variance
#@ param relative whether to make the variance relative or absolute
#@ param plot which panels to plot. Can be any of the followings (default is all):
# "var boxplot" = variance per group;
# "var by n" = variance per sample size;
# "log var boxplot" = logged variance per group;
# "log var by n" = logged variance per sample size;
# "corrected var boxplot" = logged variance divided by logged sample sizel;
# "corrected var by n" = logged variance per logged sample size divided by logged sample size;
# "standard error" = variance per group divided by sqrt(n);
# "log standard error" = logged standard error;

plot.decompose.var <- function(data, posteriors, group.cols, obs.col = "red", relative = FALSE, plot = c("var boxplot", "var by n", "log var boxplot", "log var by n", "corrected var boxplot", "corrected var by n", "standard error", "log standard error"), ...) {
    ## Get the model variance
    model_variance <- MCMCglmm.variance(posteriors, scale = relative)
    colnames(model_variance) <- c(name.subsets(data), "residuals")
    ## Get the data variance
    if(!relative) {
        obs_var <- sd(unlist(data$matrix[[1]][, c(data$call$dimensions)]))^2
    }
    var_name <- ifelse(relative, "relative variance", "variance")
    if(missing(group.cols)) {
        group_cols <- rep("grey", ncol(model_variance))
    }
    sample_sizes <- c(size.subsets(data), "residuals" = nrow(data$matrix[[1]]))
    median_variances <- apply(model_variance, 2, median)

    ## Plotting all these with logs
    if(length(plot) > 1) {
        par(mfrow = c(ceiling(length(plot)/2), 2))
    }

    ## Overall results
    if("var boxplot" %in% plot) {
        boxplot(model_variance, main = paste0(var_name, " per terms"), xlab = var_name, col = group.cols, horizontal = TRUE, las = 1)
        if(!relative) {
            abline(v = obs_var, col = obs.col, lwd = 2)
        }
        legend("topright", legend = "data variance", col = obs.col, lty = 1, lwd = 2)
    }

    ## Results by sample size
    if("var by n" %in% plot) {
        plot(y = median_variances, x = sample_sizes, ylab = paste0("median ", var_name), xlab = "sample size", pch = 19, col =  group.cols, main = paste0(var_name, " by sample size"))
        if(!relative) {
            points(y = obs_var, x = sample_sizes[length(sample_sizes)], col = obs.col, pch = 21, cex = 2)
        }
        model <- lm(median_variances ~ sample_sizes)
        fit <- paste0("lm fit (adj.R^2) = ", round(summary(model)$adj.r.squared, 3))
        legend("topright", legend = fit, lty = 1)
    }

    ## Logged results
    if("log var boxplot" %in% plot) {
        boxplot(apply(model_variance, 2, log), main = paste0(var_name, " per terms (logged)"), xlab = paste0(var_name, "(logged)"), col = group.cols, horizontal = TRUE, las = 1)
        if(!relative) {
            abline(v = log(obs_var), col = obs.col, lwd = 2)
        }
    }

    ## Results log logged
    if("log var by n" %in% plot) {
        plot(y = log(median_variances), x = log(sample_sizes), ylab = paste0("median ", var_name, " (log)"), xlab = "sample size (log)", pch = 19, col =  group.cols, main = paste0("log ", var_name, " by sample size"))
        if(!relative) {
            points(y = log(obs_var), x = log(sample_sizes[length(sample_sizes)]), col = obs.col, pch = 21, cex = 2)
        }
        model <- lm(log(median_variances) ~ log(sample_sizes))
        abline(model$coefficients)
        fit <- paste0("lm fit (adj.R^2) = ", round(summary(model)$adj.r.squared, 3))
        legend("topright", legend = fit, lty = 1)
    }

    ## Boxplots of log logged sample size corrected results
    if("corrected var boxplot" %in% plot) {
        boxplot(apply(model_variance, 2, log)/log(sample_sizes), main = paste0(var_name, " per terms (logged)\ndivided by log(sample size)"), xlab = paste0(var_name, "(logged)/log(n)"), col = group.cols, horizontal = TRUE, las = 1)
        if(!relative) {
            abline(v = log(obs_var)/log(sample_sizes[length(sample_sizes)]), col = obs.col, lwd = 2)
        }
    }

    ## Results log logged / log sample size
    if("corrected var by n" %in% plot) {
        plot(y = log(median_variances)/log(sample_sizes), x = log(sample_sizes), ylab = paste0("median ", var_name, " (log) / log(sample size)"), xlab = "sample size (log)", pch = 19, col =  group.cols, main = paste0("corrected", var_name, " by sample size"))
        if(!relative) {
            points(y = log(obs_var)/log(sample_sizes[length(sample_sizes)]), x = log(sample_sizes[length(sample_sizes)]), col = obs.col, pch = 21, cex = 2)
        }
        model <- lm(log(median_variances)/log(sample_sizes) ~ log(sample_sizes))
        abline(model$coefficients)
        fit <- paste0("lm fit (adj.R^2) = ", round(summary(model)$adj.r.squared, 3))
        legend("topright", legend = fit, lty = 1)
    }

    ## Boxplot of standard error
    if("standard error" %in% plot) {
        boxplot(model_variance/sqrt(sample_sizes), main = "Standard error per terms", xlab = "standard error", col = group.cols, horizontal = TRUE, las = 1)
        if(!relative) {
            abline(v = obs_var/sqrt(sample_sizes[length(sample_sizes)]), col = obs.col, lwd = 2)
        }
    }

    if("log standard error" %in% plot) {
        boxplot(log(model_variance/sqrt(sample_sizes)), main = "Standard error per terms (logged)", xlab = "log standard error", col = group.cols, horizontal = TRUE, las = 1)
        if(!relative) {
            abline(v = log(obs_var/sqrt(sample_sizes[length(sample_sizes)])), col = obs.col, lwd = 2)
        }
    }
}
```

```{r, echo = FALSE}
## Plotting all the variance elements
plot.decompose.var(first_model_results, first_model_run, group.cols = c(clade_cols, "residuals" = "darkgrey"), plot = 1:8, relative = FALSE)
```

@@

For this model we can use the charadriiformes example data from `dispRity` where the groups are slightly different sizes (but equal-ish) but based on biological data.

```{r, echo = FALSE}
data(charadriiformes)
## Same but selecting only the three first random terms
chara_data <- MCMCglmm.subsets(data       = charadriiformes$data,
                               posteriors = charadriiformes$posteriors,
                               tree       = charadriiformes$tree,
                               group      = MCMCglmm.levels(charadriiformes$posteriors)[1:4],
                               rename.groups = c("gulls", "plovers", "sandpipers", "phylogeny"))
```

This is what it looks like:

```{r, echo = FALSE}
## Set up the clade colours
clade_cols <- c("gulls" = "blue", "plovers" = "orange", "sandpipers" = "darkgreen", "phylogeny" = "grey")
## Plot the model
covar.plot(chara_data, col = clade_cols, ellipses = mean, legend = TRUE, lwd = 2, points.cex = 0.5)
```

And this is what the variances look like:

```{r, echo = FALSE}
plot.decompose.var(chara_data, charadriiformes$posteriors, group.cols = c(clade_cols, "residuals" = "darkgrey"))
```

@@

This is the big model run just on 2D and only with the super orders levels.
The differences with the true results are due to it:
 * not being the same dataset!
 * not having converged...

```{r, echo = FALSE}
## Load the models from the local files
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/chains_2D_testing/params_shapespace_2D_9levels_20k_chain1_20.rda")
model_1_20 <- shapespace_allbirds_lvl_superorder_order_2D
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/chains_2D_testing/params_shapespace_2D_9levels_20k_chain21_40.rda")
model_21_40 <- shapespace_allbirds_lvl_superorder_order_2D
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/chains_2D_testing/params_shapespace_2D_9levels_20k_chain41_60.rda")
model_41_60 <- shapespace_allbirds_lvl_superorder_order_2D
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/chains_2D_testing/params_shapespace_2D_9levels_20k_chain61_80.rda")
model_61_80 <- shapespace_allbirds_lvl_superorder_order_2D
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/chains_2D_testing/params_shapespace_2D_9levels_20k_chain81_100.rda")
model_81_100 <-shapespace_allbirds_lvl_superorder_order_2D
## Combine all the models
model <- combine.mini.chains(unlist(list(model_1_20, model_21_40, model_41_60, model_61_80, model_81_100), recursive = FALSE))

## Load the data
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order.rda")
## Select the data
shapespace <- shapespace_allbirds_lvl_superorder_order[[1]]$space
## Clean garbage
rm(shapespace_allbirds_lvl_superorder_order)

## Set up the dispRity object
birds_data <- MCMCglmm.subsets(data       = shapespace[, -c(3:8)],
                               posteriors = model,
                               group      = MCMCglmm.levels(model)[-10],
                               rename.groups = c(levels(shapespace$level1)[-1], "phylogeny"))
## Set up the clade colours
load("../Data/Processed/tip_colours_super_orders.rda")
clade_cols <- c(tip_colours_super_orders, "phylogeny" = "grey")
## Plot the model
covar.plot(birds_data, col = clade_cols, ellipses = mean, legend = TRUE, lwd = 2, points.cex = 0.5)
```

```{r, echo = FALSE}
## Plotting the variance with different data
plot.decompose.var(birds_data, model, group.cols = c(clade_cols, "residuals" = "darkgrey"))
```

@@

```{r, echo = FALSE}
## Load the data
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order.rda")
## Select the data
shapespace <- shapespace_allbirds_lvl_superorder_order[[1]]$space
## Clean garbage
rm(shapespace_allbirds_lvl_superorder_order)

## Load the posteriors
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order.MCMCglmm")
model <- shapespace_allbirds_lvl_superorder_order[[1]]

## Get the colourss
load("../Data/Processed/tip_colours_orders.rda")
clade_cols <- c(tip_colours_super_orders, tip_colours_orders, "phylogeny" = "grey")

## Set up the dispRity object
full_model <- MCMCglmm.subsets(data       = shapespace,
                               posteriors = model,
                               group      = MCMCglmm.levels(model)[-37],
                               rename.groups = c(levels(shapespace$level1)[-1], levels(shapespace$level2)[-1], "phylogeny"))

covar.plot(full_model, col = clade_cols, ellipses = mean, legend = TRUE, lines.lty = c(rep(1, length(levels(shapespace$level1)[-1])), rep(2, length(levels(shapespace$level2)[-1])), 1), points = FALSE)
```

```{r, echo = FALSE}
## Plotting the variance with different data
plot.decompose.var(full_model, model, group.cols = c(clade_cols, "residuals" = "darkgrey"), plot = 4)
```
